Twisted eleven-dimensional supergravity

### 2021-11-04 intro.tex

For many years, twisting constructions were motivated by the goal of producing topological field theories, and correspondingly emphasized the role of particular modifications of  Lorentz symmetry via ``twisting homomorphisms'' designed to produce scalar supercharges.
From a more modern perspective, though, twisting a supersymmetric field theory is just a systematic way of taking invariants with respect to a fixed supercharge. This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.\footnote{More generally, one could consider ``omega backgrounds'' by taking the derived invariants of a more general subalgebra in which the odd part is not necessarily abelian.}
The variety of appropriate square-zero elements was studied systematically in~\cite{NV}, and has deep relations not only to the  classification of  twists, but to the construction  of supersymmetric field theories via the pure spinor formalism~\cite{Cederwall,EHSW}. The name ``pure spinor'' originates because the  variety of  square-zero elements always contains a minimal stratum that is related to the space of Cartan pure spinors; in turn, these correspond to choices of complex structure on the  spacetime, at least when the dimension is even. 
As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lfloor d/2\rfloor$ of the translations act nontrivially. Other twists can be understood as further twists of this holomorphic theory.
The importance and interest of holomorphic twists was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite{NekThesis}. (Constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.)

@@

\subsection*{Acknowledgements}
We warmly thank I.~Brunner, M.~Cederwall, K.~Costello, R.~Eager, O.~Gwil\-liam, F.~Hahner, J.~Huerta, H.~Loosen, N.~Paquette, S.~R\"osch, J.~Walcher for conversation and inspiration of all kinds. I.S. and B.W. thank the University of Heidelberg, B.W. thanks the University of Edinburgh and the Mathematisches Forschungsinstitut Oberwolfach, and I.S. thanks the Krameterhof for hospitality while portions of this work were being completed. The work of S.R. is supported by the Perimeter Institute for Theoretical Physics. Research at Perimeter Institute is supported in part by the Government of Canada, through the Department of Innovation, Science and Economic Development Canada, and by the Province of Ontario, through the Ministry of Colleges and Universities.
The work of I.S. is supported by the Free State of Bavaria. The work of B.W. is supported by the University of Edinburgh.
% Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of the funding agencies.

>>>>

For many years, twisting constructions were motivated by the goal of producing topological field theories, and correspondingly emphasized the role of particular modifications of  Lorentz symmetry via ``twisting homomorphisms'' designed to produce scalar supercharges.
From a more modern perspective, though, twisting a supersymmetric field theory is just a systematic way of taking invariants with respect to a fixed supercharge. This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.\footnote{More generally, one could consider ``omega backgrounds'' by taking the derived invariants of a more general subalgebra in which the odd part is not necessarily abelian.}
The variety of appropriate square-zero elements was studied systematically in~\cite{NV}, and has deep relations not only to the  classification of  twists, but to the construction  of supersymmetric field theories via the pure spinor formalism~\cite{Cederwall,EHSW}. The name ``pure spinor'' originates because the  variety of  square-zero elements always contains a minimal stratum that is related to the space of Cartan pure spinors; in turn, these correspond to choices of complex structure on the  spacetime, at least when the dimension is even. 
As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lfloor d/2\rfloor$ of the translations act nontrivially. Other twists can be understood as further twists of this holomorphic theory.
The importance and interest of holomorphic twists of supersymmetric gauge theories was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite[for example]{NekThesis,BCOV}.
Si Li pushed applications of holomorphic QFT further in his work on the higher genus $B$-model (see~\cite{SiThesis}, and later \cite{CLbcov1} together with Costello). 
In the physics literature, further constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.

@@

\subsection*{Acknowledgements}
We warmly thank I.~Brunner, M.~Cederwall, K.~Costello, R.~Eager, C.~Elliott, D.~Gaiotto, O.~Gwil\-liam, F.~Hahner, J.~Huerta, H.~Loosen, S.~Li, N.~Paquette, S.~R\"osch, J.~Walcher, P.~Yoo for conversation and inspiration of all kinds. I.S. and B.W. thank the University of Heidelberg, B.W. thanks the University of Edinburgh and the Mathematisches Forschungsinstitut Oberwolfach, and I.S. thanks the Krameterhof for hospitality while portions of this work were being completed. The work of S.R. is supported by the Perimeter Institute for Theoretical Physics. Research at Perimeter Institute is supported in part by the Government of Canada, through the Department of Innovation, Science and Economic Development Canada, and by the Province of Ontario, through the Ministry of Colleges and Universities.
The work of I.S. is supported by the Free State of Bavaria. The work of B.W. is supported by the University of Edinburgh.
% Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of the funding agencies.
